Enforced Invariant Confluence

### 2018-09-19 doc/paper/sections/related_work.tex
Added CRDT section to related work.
From reviewer 11:

> A clear connection to what CRDTs are within scope would improve the
> contribution of this paper.

and

> You make a connection to Shapiro et al.'s work on CRDT and use a few
> examples that are popular (e.g. PN-Counter), but can you go further
> and connect to more complex structures like Sequence. This will allow
> you to reach a broader audience and let them clearly understand the
> broader implication of this work. (BTW, nice discussion of PK-FK).

Previously, we had a paragraph on CRDTs in the related works section. I
cut it out bec

% \textbf{CRDTs.}
% CRDTs~\cite{shapiro2011conflict, shapiro2011comprehensive} are distributed
% semilattices with inflationary update methods. Due to their algebraic
% properties, CRDTs can be replicated with strong eventual consistency without
% the need for any coordination. Our definition of distributed objects and our
% \invariantconfluence{} system model are inspired directly by the corresponding
% definitions and system models in~\cite{shapiro2011conflict}. Also, an
% \invariantconfluent{} object does not necessarily have to be eventually
% consistent, so it is natural (though not necessary) to use CRDTs as
% \invariantconfluent{} distributed objects, achieving a combination of eventual
% consistency and invariant preservation. Our criteria in
% \thmref{LatticeProperty} also borrow ideas from CRDTs, exploiting the nice
% algebraic properties of semilattices.

>>>>

\textbf{CRDTs.}
CRDTs~\cite{shapiro2011conflict, shapiro2011comprehensive} are distributed
semilattices with inflationary update methods. Due to their algebraic
properties, CRDTs can be replicated with strong eventual consistency without
the need for any coordination. Our definition of distributed objects and our
\invariantconfluence{} system model are inspired directly by the corresponding
definitions and system models in~\cite{shapiro2011conflict}.
%
CRDTs are eventually consistent but may not preserve invariants. Conversely,
\invariantconfluent{} objects preserve invariants but may not be eventually
consistent. Thus, it is natural (though not necessary) to use CRDTs as
distributed objects. If a CRDT is determined to be \invariantconfluent{} with
respect to a particular invariant and set of transactions, then it achieves a
combination of strong eventual consistency and invariant preservation. Any CRDT
(e.g., counters, sets, graphs, sequences) can be used for this purpose.
%
Finally, our criteria in \thmref{LatticeProperty} also borrow ideas from CRDTs,
exploiting the nice algebraic properties of semilattices.
